The error in Bayesian phylogenetic reconstruction when speciation co-occurs

### 2019-12-09 razzo-hypotheses.tex
Updates from Overleaf

$\mathcal{H}_4$: RJCB expects that, on average, the inference error is equal for
parameter settings with an equal $\lambda$, $\nu$ and $q$, i.e. extinction
has no effect on the error made, because extinction affects all species equally. 
\richel{figure 1a and b, or a new figure}

@@

$\mathcal{H}_7$: RJCB expects that the nLTT statistic between a true and twin
tree at the start of the pipeline,
will correlate strongly with the difference
between the higest posterior density (HPD) of the 
errors of the true and twin tree 
generated at the end of the pipeline. 
This hypothesis
stems from the idea of assuming a setup without noise; that is, with
a DNA alignment of infinite length. From such a DNA alignment 
with infinite information, the MCMC
is able to infer the close-to-correct phylogeny.
\richel{if this is true, we can use this shortcut (instead of running
multiple pirouette replicates) to draw stronger conclusions}
\richel{figure 5}

@@

>>>>

$\mathcal{H}_4$: RJCB expects that, on average, the inference error is equal for
parameter settings with an equal $\lambda$, $\nu$ and $q$, i.e. extinction
has no effect on the error made, because extinction affects all species equally. 
\richel{figure 1a and b, or a new figure}
\giovanni{A higher extinction rate increases variance and tend to reduce to number of taxa in the tree. According to your other hypotheses (e.g. H5) these effects do affect the inference. Therefore you need to adjust for these variables to prove your hypothesis.}

@@

$\mathcal{H}_7$: RJCB expects that the nLTT statistic between a true and twin
tree at the start of the pipeline,
will correlate strongly with the difference
between the highest posterior density (HPD) of the 
errors of the true and twin tree 
generated at the end of the pipeline. 
This hypothesis
stems from the idea of assuming a setup without noise; that is, with
a DNA alignment of infinite length. From such a DNA alignment 
with infinite information, the MCMC
is able to infer the close-to-correct phylogeny.
\richel{if this is true, we can use this shortcut (instead of running
multiple pirouette replicates) to draw stronger conclusions}
\giovanni{I can agree with the principle. However there are also other factors that you might overlook with such approximation. It might be useful, though, for a fast comparison to have a preliminary idea, if the hypothesys will be confirmed by the experiment.}
\richel{figure 5}

@@

$\mathcal{H}_9$: GL expects a positive correlation between $\nu \, q(1-q)$ and the error made by the inference process. This is due to the fact that this factor regulates the variance of the underlying binomial distribution that regulates multiple births events.
